Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-09 bbbq_article.tex
Remove 'haplotype_freq_vs_f_tmh_epitopes'

HIERO

\paragraph{Data}
As a data source, multiple
NCBI (\url{https://www.ncbi.nlm.nih.gov/}) databases are used:
'gene' to find the gene names of membrane proteins, 
'dbSNP' (\cite{sherry2001dbsnp}) for SNPs associated with those genes
and 'protein' to obtain the sequence of proteins that SNPs act upon.
The 'dbSNP' contains 650 million 
catalogued non-redundant humane variations (called RefSNPs,
/url{https://www.ncbi.nlm.nih.gov/snp/docs/RefSNP_about/}).
It is estimated that approximately ten percent (ranging from 2 to 36 percent) 
are artifacts (\cite{carlson2003additional, cutler2001high, gabriel2002structure, mitchell2004discrepancies, musumeci2010single, reich2003quality}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relation between haplotype frequency and TMH over-representation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There is no relation between haplotype frequency and TMH over-representation.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{haplotype_freq_vs_f_tmh_epitopes/haplotype_perc_vs_f_tmh_binders.png}
  \caption{
    Relation between genotype frequency and the percentage
    of binders that are TMH for the 21 MHC-II haplotypes
  }
  \label{fig:haplotype_perc_vs_f_tmh_binders}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{haplotype_freq_vs_f_tmh_epitopes/phenotype_freq_vs_f_tmh_binders.png}
  \caption{
    Relation between phenotype frequency and the percentage
    of binders that are TMH for the 21 MHC-II haplotypes
  }
  \label{fig:phenotype_freq_vs_f_tmh_binders}
\end{figure}

>>>>

\paragraph{Data}

As a data source, multiple
NCBI (\url{https://www.ncbi.nlm.nih.gov/}) databases are used:
'gene' to find the gene names of membrane proteins, 
'dbSNP' (\cite{sherry2001dbsnp}) for SNPs associated with those genes
and 'protein' to obtain the sequence of proteins that SNPs act upon.
The 'dbSNP' contains 650 million 
catalogued non-redundant humane variations (called RefSNPs,
\url{https://www.ncbi.nlm.nih.gov/snp/docs/RefSNP_about/}).
It is estimated that approximately ten percent (ranging from 2 to 36 percent) 
are artifacts (\cite{carlson2003additional, cutler2001high, gabriel2002structure, mitchell2004discrepancies, musumeci2010single, reich2003quality}).

@@
